---
title: "spata basic analysis"
author: "Richard J Beck"
date: "`r Sys.Date()`"
output: html_document
---

The goal of this pipeline is to run thru some of the spata tutorials to gain a better understanding of how they are processing their data.

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir="~/../repos/scanalyzR/")
```

```{r}

library(SPATA2)

```

COPY NUMBER VARIATIONS:

```{r}


x <- loadExampleObject(sample_name = "UKF269T")

# only histology
plotSurface(x, pt_alpha = 0)


```

Uses infercnv to assess CNAs. What really gets me is that the CNA values are so low! So e.g. we have these CNA peaks centered on about 0.95 & 1.05. So does this imply a really low tumor cell fraction?? What further piz
```{r}

x <-
  runCNV(
    object = x,
    # the directory must exist in your file system
    directory_cnv_folder = "data/scRNAseq/tmp/", 
    cnv_prefix = "Chr"
    )

plotCnvHeatmap(object = x)

plotCnvLineplot(
  object = x,
  n_bins_bcsp = 1000,
  n_bins_genes = 1000,
  )

plotSurface(
  object = x, 
  color_by = "Chr7", 
  pt_clrsp = "Reds"
)

```
Lets run infercnv on one of scRNAseq data samples.


```{r}
library(ggplot2)
x <- read.csv("data/tmp/269_T.csv")

p <- ggplot(x,aes(x=xcoord,y=ycoord,color=preds))+
  scale_color_viridis_c()+
  geom_point()
p
```
```{r}

dir <- "data/tmp/Spatial_GBM_PloiViT/"
x <- lapply(list.files(dir),function(fi) read.csv(paste0(dir,fi)))

for(i in x){
  p <- ggplot(i,aes(x=xcoord,y=ycoord,color=preds))+
  scale_color_viridis_c()+
  geom_point()
plot(p)
}
```

```{r}
x <- readRDS("data/tmp/Boston_269_T.RDS")
df <- x@coordinates$'269_T'
f <- x@fdata$'269_T'
f <- f[,c("barcodes","pred.tumor","Nr_of_cells")]

df <- merge(f,df,by=c("barcodes"))

p <- ggplot(df,aes(x=x,y=y,color=pred.tumor))+
  geom_point()+
  scale_color_viridis_c()
p

p <- ggplot(df,aes(x=x,y=y,color=Nr_of_cells))+
  geom_point()+
  scale_color_viridis_c()
p

```